Computing Vowel Elision in Yoruba Collocations

### 2023-04-20 paper.tex
Updates from Overleaf

We now describe key details of our implementation. The full source code may be
found at \href{https://github.com/hemantgouni/linguistics-capstone}{github.com/hemantgouni/linguistics-capstone}.
Starting with the basics, Figure \ref{fig:impl-deletion} shows both our
representation of Yoruba words and our simple handling of deletion.
Specifically, a word is represented as a list of segments; this is denoted by
\texttt{Vec<Segment>} on line 2.
At this point, it is reasonable to ask: why not represent words simply
as a list of characters? What's the difference between a character and a segment?
This reflects a complication in computers' handling of text beyond the
simple English characters covered by the ASCII character encoding. Unicode, an
improvement of ASCII that handles many more languages beyond those which use the
Latin alphabet, would consider the accent mark and letter \textipa{O} in \textipa{\'O},
to be separate characters, and not part of the same. We must sidestep this issue by
parsing words into \textit{graphemes}, which accounts for the intuitive notion
of what a character is: \textipa{\'O} is a single grapheme.

>>>>

We now describe key details of our implementation. The full source code may be
found at \href{https://github.com/hemantgouni/linguistics-capstone}{github.com/hemantgouni/linguistics-capstone}.
Starting with the basics, Figure \ref{fig:impl-deletion} shows both our
representation of Yoruba words and our simple handling of deletion.
Specifically, a word is represented as a list of segments; this is denoted by
\texttt{Vec<Segment>} on line 2.
At this point, it is reasonable to ask: why not represent words simply
as a list of characters? What's the difference between a character and a segment?
This reflects a complication in computers' handling of text beyond the
simple English characters covered by the ASCII character encoding. Unicode, an
improvement of ASCII that handles many more languages beyond those which use the
Latin alphabet, would consider the accent mark and letter \textipa{O} in \textipa{\'O},
to be separate characters and not parts of the same. We must sidestep this issue by
parsing words into \textit{graphemes}, which accounts for the intuitive notion
of what a character is: \textipa{\'O} is a single grapheme.
